---
title: "Brief take on HTML"
author: "Y.T Lin"
date: "2019/12/11"
output: html_document
---

```{r basic setup, message=FALSE, echo=TRUE, eval=T}
library(dplyr); library(stringr); library(ggplot2); library(plotly); library(lubridate); library(readr); library(tidyr); library(showtext); library(colorspace); library(scales)
font_add("QYuan","cwTeXQYuan-Medium.ttf") # 新增字體
showtext_auto(enable=TRUE) #啟用字體
theme_set(theme_classic())
knitr::opts_chunk$set(out.width='80%', fig.asp=.75, fig.align='center', fig.showtext=T)
```

## Brief take on HTML  
\  

```{r source this}
source("https://www.dropbox.com/s/mdx4777ugnluspz/webApplications.R?dl=1")

# add some functions to help with your html script generation
```  
\  

```{r head start for html}

# create a html file "index.html" with the directory webProject0
project_html_create(
  main_file="index.html",
  type="plain", # or bs : bootstrap
  dirlib="webProject0",
  structure=c(
    "js",
    "css",
    "assets")
)
```  
\  

The above chunks covers the section of CH 7 till 7.1.7.  
Most of the work and lecture codes are done in the webProject0/index.html
You should read that as well.  
\  

### 7.1.7.1 External CSS file  
\  

We will now enter the editing of the styling of a html file. We complete the editing with a CSS file. First, we need to create a css file.  
\  

```{r creating a CSS file}
file.edit("my.css")
```  
\  

The later lecture codes are performed in the my.css file. You'll have to read it.  
\  

## 7.1.9 SVG  
\  

Let's try to do some modification ona SVG file.  
\  

```{r get the SVG}
dir.create(
  "./1211"
)
download.file("https://raw.githubusercontent.com/tim8537099/course-108-1-inclass-datavisualization/master/example/tet.Rmd",
              destfile="1211/tet.Rmd"
)
download.file("https://github.com/tim8537099/course-108-1-inclass-datavisualization/blob/master/example/plot_us.Rda?raw=true",
              destfile="1211/plot_us.Rda"
)

file.edit("1211/tet.Rmd")
```