---
title: "課堂練習 2019 09 18"
author: "Y.T Lin"
date: "2019/9/18"
output: html_document
---
```{r basic setup, message=FALSE, echo=TRUE, eval=T}
library(dplyr); library(stringr); library(ggplot2); library(plotly); library(lubridate); library(readr); library(tidyr); library(showtext)

#font_add("QYuan","cwTeXQYuan-Medium.ttf") # 新增字體
showtext_auto(enable=TRUE) #啟用字體
theme_set(theme_classic())
knitr::opts_chunk$set(out.width='80%', fig.asp=.75, fig.align='center', fig.showtext=T)
```

  In class code for 2019_09_18. 

### Data Cleaning

```{r Generating data.frame}
################# List then Transformed to data.frame #################
StuList <- list(
  次序=c(1,2,3,4,5,6,7,8),
  學號=c(172,214,322,425,517,833,752,114),
  姓名=c("小明","大雄","胖虎","小新","大白","阿華","小英","阿美"),
  性別=c("男","男","男","女","女","男","女","男"),
  成績=c(80,42,90,82,50,77,30,90)
)
StuList 

as.data.frame(StuList) -> StuDFfromList
StuDFfromList

 ################# Generating a Data.frame #######################

StuDF <- data.frame(
  次序=c(1,2,3,4,5,6,7,8),
  學號=c(172,214,322,425,517,833,752,114),
  姓名=c("小明","大雄","胖虎","小新","大白","阿華","小英","阿美"),
  性別=c("男","男","男","女","女","男","女","男"),
  成績=c(80,42,90,82,50,77,30,90)
)
StuDF 

  # str(StuDF)
```


```{r class() and typeof()}
################ class() and typeof() ###############
  ## Observing the class and type of an environment object (class != type)

class(StuDF) # data.frame
typeof(StuDF) # list

class(StuList) # list
typeof(StuList) # list
```

```{r length() and nrow()}
############# length() and nrow() #################

  ## to find out the "size" of the dataset
length(StuDF) # 5
nrow(StuDF) # 8
```

```{r str()}
str(StuDF) # check the structure of the dataset 
head(StuDF) # show the first 5 obs.
tail(StuDF) # show the last five obs.
```

```{r slice()}
StuDF
dplyr::slice(StuDF, 1:3) # slice() is to show a portion of the dataset
slice(StuDF, 4:5)
slice(StuDF, n()) # n() is to show how many obs. are there in the dataset.

## to show the last 2 obs.
dplyr::slice(StuDF, (n()-1):n())
```

```{r slice practice}
StuDF
slice(StuDF,-5:-7) # Delete the 5,6, and 7 obs.
slice(StuDF, -(5:7))
slice(StuDF, c(-5,-6,-7))

```

```{r}
slice(StuDF, c(1,4,8))
```

```{r 106 student slice}
collegeData <- read_csv("https://raw.githubusercontent.com/tpemartin/github-data/master/103_student.csv")

str(collegeData)

dplyr::slice(collegeData, 1:4)
dplyr::slice(collegeData, (n()-2):n())
dplyr::slice(collegeData, 101:110)
```

#### Mutate() and Transmute()
```{r mutate and transmute}
StuDF
mutate(StuDF,
       調分後成績=成績+10) # retain other variables as well

transmute(StuDF,
       調分後成績=成績+10) # Only leave the new created variable

## Remember to save as a new object

## Not using the dplyr PKG functions (Mutate)
StuDF$調分後成績 <- StuDF$成績+10

```

```{r mutate practice}
collegeData <- mutate(collegeData,
       男生 = 一年級男生 + 二年級男生 + 三年級男生 + 四年級男生, 
       女生 = 一年級女生 + 二年級女生 + 三年級女生 + 四年級女生,
       男女生比 = 男生 / 女生)

collegeData[1:10,] 
```

#### Summarise ()

```{r summarise}
## to see the check the basic stats.

StuDF
summarise(StuDF,
        平均成績=mean(成績),
        最高分=max(成績),
        最低分=min(成績))
```

```{r change summarise to mutate}
mutate(StuDF,        
       平均成績=mean(成績),
        最高分=max(成績),
        最低分=min(成績))
```

```{r summarise practice}
summarise(StuDF, 
          最高分=max(成績),
          最低分=min(成績),
          調整後成績 = (最高分 - 最低分)/5)

## Generate the adjusted scores with mutate
mutate(StuDF, 
       調整後分數 = 成績 + (max(成績) - min(成績))/5)
```

#### Select

```{r select}
## Select() is for choosing variables


StuDF2 <- mutate(StuDF,
        平均成績=mean(成績),
        最高分=max(成績),
        最低分=min(成績))

StuDF2

names(StuDF2) # Check the variables' names
select(StuDF2,
       姓名,學號,成績,調分後成績) # snatch out the desired variables

select(StuDF2,
       -次序,-性別,-最高分,-最低分) # NOT choosing the varaibles

```

select可搭配select helpers:
starts_with(): Starts with a prefix.

ends_with(): Ends with a suffix.

contains(): Contains a literal string.

matches(): Matches a regular expression.

num_range(): Matches a numerical range like x01, x02, x03.

one_of(): Matches variable names in a character vector.

everything(): Matches all variables.

last_col(): Select last variable, possibly with an offset.

```{r some examples for the select helpers}
select(StuDF2,
       次序,性別,
       contains("最")) # choose 次序 性別 and all vars containing the word "最"

select(StuDF2,
       -次序,-性別,
       -contains("最")) 
```

```{r select prac. collegeData}
select(collegeData, contains("男生"))
```


#### Filter
 
 To Choose the obs. that matches to the description
 
```{r filter}
StuDF

# logical vector
logiChoose <- c(
  F,F,F,T,T,F,T,F
)

# 使用logical vector選擇所要觀測值"女"
StuDF[logiChoose,]

## Using filter()

StuDF %>% filter( 性別 == "女")

## Using which() and the logical Vector
logiChoose
which(logiChoose) # 4, 5, 7

slice(
  StuDF,which(logiChoose)
)

  # Logical Predicate
StuDF$性別=="女" # logical predicate

logiChoose <- StuDF$性別=="女"
StuDF[logiChoose,]

## Logical predicate can be generated by: 
  ## Relation Operator: a > b
  ## Logical Operater: a|b (or), a & b , (a & b) ! c (! = NOT)

(StuDF$性別=="女" & StuDF$成績>60) -> logiChoose2
logiChoose2

StuDF[logiChoose2,]

## Back to using filter()

filter(StuDF, 性別 == "女")

 ## Multiple descriptions
filter(StuDF,
       (性別=="女" & 成績>60))

    # OR

filter(StuDF,
       性別=="女",
       成績>60) # 多個AND條件可用,分隔
```

```{r filter prac. collegeData}
collegeData %>% filter(縣市名稱 == "30 臺北市")

collegeData %>% filter(縣市名稱 == "30 臺北市" | 縣市名稱 == "01 新北市")

# Using %in%
collegeData %>% filter(縣市名稱 %in% c("30 臺北市", "01 新北市"))
```

#### group_by() 分群計算

```{r group_by}
StuDF_by性別 <- group_by(StuDF, 性別)

summarise(StuDF_by性別,
        平均成績=mean(成績),
        最高分=max(成績),
        最低分=min(成績))

  # change score by different gender groups 

mutate(
  StuDF_by性別,
  最高分=max(成績),
  最低分=min(成績),
  調分大小=(最高分-最低分)/5,
  調分後成績=成績+調分大小
) -> StuDF_依性別調分

StuDF_依性別調分

  ### Group by gender and score
StuDF_by性別成績 <- group_by(StuDF, 性別, (成績>75))

summarise(StuDF_by性別成績,
          平均成績=mean(成績),
          人數=n())

## Use ungroup() 

ungroup(StuDF_依性別調分) -> 
  StuDF_調分後
```

```{r group_by prac.collegeData}

  collegeData %>% 
    group_by(縣市名稱, 體系別, 等級別) %>%
    summarise(一年級男生總數 = sum(一年級男生),
            一年級女生總數 = sum(一年級女生),
            學校數目 = length(unique(學校代碼)))
    

```


#### 1.3 Pipe Operators

%>% pipe operator:

* 預設：%>% 把它左邊（LHS）的物件流入它右邊（RHS）函數的argument第一個位置。 )

* 若要流入右邊函數的「非」第一位置argument，則用.在右邊函數中標示。

* %>% 可進行串接，則下一個%>%會以上個函數輸出結果當做新的LHS物件。

```{r piping prac collegedata}
collg <- collegeData %>% 
  group_by(等級別, 縣市名稱) %>%
  dplyr::summarise(一年級男生總數 = sum(一年級男生),
                   一年級女生總數 = sum(一年級女生),
                   一年級男女比 = (一年級男生總數 / 一年級女生總數)) %>%
  ungroup() 

locmax <- collg[which.max(collg$一年級男女比), ]
locmax
```

```{r piping prac. transcript}
# Get transcriptDataFinal

load(url("https://www.dropbox.com/s/duh5aaqgl2f5m3z/loopTranscriptData.Rda?raw=1"))

# 計算每位學生每個學期的平均成績
transcriptDataFinal %>%
    group_by(學號,學年,學期) %>%
  dplyr::summarise(
    平均成績=sum(學期成績*學分數)/sum(學分數)
  )

#計算每位學生每學期學分數在必/選/通 三類的學分數比重。

#學屆為100（即100學年入學）的學生，各系學生在學所修總學分數之中位數，何系最高？
```