---
title: "課堂練習11_13"
author: "Y.T Lin"
date: "2019/11/13"
output: html_document
---

```{r basic setup, message=FALSE, echo=TRUE, eval=T}
library(dplyr); library(stringr); library(ggplot2); library(plotly); library(lubridate); library(readr); library(tidyr); library(showtext); library(colorspace); library(scales)
font_add("QYuan","cwTeXQYuan-Medium.ttf") # 新增字體
showtext_auto(enable=TRUE) #啟用字體
theme_set(theme_classic())
knitr::opts_chunk$set(out.width='80%', fig.asp=.75, fig.align='center', fig.showtext=T)
```

### Ch 5.3 Simple Features

We explore the `simple features package`. Some addition features can be added onto the map we've drawn in the previous lecture.  
\  

```{r library}
library(sf)
```  
\  

The process of the simple features object can be divided into 3 steps:  

* Simple Feature class (`sfg class`): Transform spatial data into simple feature class datas.  

* Simple Feature column (`sfc class`): All of the `sfg` data will be combinded into a Simple Feature Column.  

* Simple Feature Object (`sf class`): The `sfc` will later be combinded with the original spatial data and will have the class of `sf`.  

\  

We start by constructing a `sfg` data.  
\  

### Ch 5.5.1 Geometry (sfg)  
\  

#### Points (st_multipoint)  
\  

```{r geometry sfg points}
# single point
point <- st_point(
  c(2,3)
)

point %>% ggplot()+geom_sf()

# multi-points
mpoint <- st_multipoint(
    rbind(c(1,0),
        c(2,3),
        c(-1,2))
)
  # rbind() to construct a dataset of points' location data
mpoint %>% ggplot()+geom_sf()
```  
\  

#### Lines (st_multilinestring)  
\  

```{r geometry sfg line}
# A single line
line <- st_linestring( 
  # Notice we used st_linestring() instead of st_multipoint()
    rbind(c(1,0),
        c(2,3),
        c(-1,2))
)

line %>% ggplot()+geom_sf()

# Multiple Lines

  # use list() and multiple rbind() to discern different linestrings
mline <- st_multilinestring(
  list(
    rbind(
      c(1,0),
      c(2,3),
      c(-1,3)),
    rbind(
      c(-2,3),
      c(-1,-1))
    )
  )

mline %>% ggplot()+geom_sf()

```  
\  

#### Polygons (st_multipolygons)  
\  

```{r Geometry sfg polygons}
# You gotta "close" the shape, by setting a point back to the "starting point"

  # Single Polygon
outer <-     
  rbind( # 外圍
    c(1,5),
    c(2,1),
    c(5,1),
    c(5,5),
    c(1,5)) # 必需自行輸入起點close it

hole <-
  rbind( # 洞
    c(2,4),
    c(3,2),
    c(4,3),
    c(2,4))  # 必需自行輸入起點close it
  
poly <- st_polygon(
  list(
    outer, 
    hole
  )
) 

poly %>% ggplot()+geom_sf()

# Multiple Polygons

  # multiple "lists" in a list to discern different polygons
outer2 <- outer + 12
hole2 <- hole + 12

mpoly <- st_multipolygon(
  list(
    list(
      outer,
      hole
    ),
    list(
      outer2,
      hole2
    )
  )
) 

mpoly %>% ggplot()+geom_sf()
```  
\  

#### Various sfg classes in one graph (st_geometrycollection)  
\  

How about a big compilation of different sfg classes features.  
I.E. (polygon + linestring), (Point + linestrings) ...etc.  
\  


```{r Geometry sfg multi classes}

st_geometrycollection(
  list(
    point, mpoint,
    line, mline,
    poly, mpoly
  )
) %>% ggplot()+ geom_sf()

```  
\  

### sfc class (Column Construction)  
\  

`st_sfc()` to construct the desired sfc class (simple feature columns).  
\  

```{r sfc class formation}
# build 2 county spatial datas (sfg data)
sfg_county1 <- st_polygon(list(
  outer,hole
))
sfg_county2 <- st_polygon(list(
  outer2, hole2
))

# form the sfc class simple feature column to write the spatial info.
sfc_county12column <- st_sfc(sfg_county1,sfg_county2)

# show the recorded spatial info.
sfc_county12column %>% ggplot+geom_sf()

  # View(sfc_county12column)  list of 2 lists(2 counties spatial info)
```  
\  

How bout we combine it with a dataframe object?
```{r combine with df set geometry}
df_county12 <- data.frame(
  name = c("county1", "county2"),
  population = c(100,107)
)

df_county12 <- df_county12 %>%
  st_set_geometry(sfc_county12column)

names(df_county12) # now we have a new column "geometry"

# str(df_county12)
# attributes(df_county12$geometry)
df_county12

df_county12 %>% ggplot() +
  geom_sf(aes(fill = population)) +
  geom_sf_text(aes(label = name))
```  
\  

### CH 5.5.4 Write a shp file

save the constructed spatial info data into a shape file `shp`.  
\  

```{r save to shp,eval = F, echo = T}
# add in a new file directory in the current working directory
dir.create("county12")
write_sf(df_county12,"county12/county12.shp")

# Of course, you can save it into a RDA file, but shp file is a more conventional file type for geometry datas.
```  
\  

A little practice to help you get started.  
\  

```{r shp file practice 1}
load(url("https://www.dropbox.com/s/uvco1te2kbs6o01/MRT_Taipei.Rda?dl=1"))

# should retrieve the `sf_mrt_tpe` object

# 其中代號’O’為「中和新蘆線」、’BL’為「板南線」，只取出此兩線，並形成一個sf data frame含有以下欄位: 路線名稱、 geometry: 代表各路線的「點、線」圖

sf_mrt_tpe %>% names

# View(sf_mrt_tpe)
str(sf_mrt_tpe) # it's a dataframe with sf class columns

# Only the BL (blue line) simple feature.
sf.mrt.blue <- sf_mrt_tpe %>% 
  select(geometry, 經過路線) %>% 
  filter(grepl("BL", sf_mrt_tpe$經過路線)) %>% # snatch out the ones with "BL"
  mutate(站號 = str_extract(經過路線, "(?<=(BL))[:digit:]+")) %>%
  arrange(站號)
  # starts with "BL" and extract all the digits  (+, means all the digits) 

# sf.mrt.blue %>% View

sf.mrt.blue.draw <- sf.mrt.blue %>% 
  st_coordinates() %>%
  st_linestring() # simple geometry feature

sf.mrt.blue.draw %>% ggplot() + geom_sf(color = "blue") # add in drawings
  
```  
\  

```{r practice 1.1}
# construct a dataframe with only BL line spatial info

df_BL <- data.frame(
  line.name = "BL"
)

sf.mrt.blue.info <- sf.mrt.blue.draw %>% st_sfc() # transform it back to a sfc 

df_BL <- df_BL %>%
  st_set_geometry(sf.mrt.blue.info)

df_BL # successfully added in

# retrieve the CRS info of the original data
mrt_crs <- sf_mrt_tpe %>%
  st_crs 

df_BL <- df_BL %>%
  st_set_crs(mrt_crs) # set it as the CRS setting for your new dataframe

df_BL
```  
\  

#### Practice of sf_Taiwan (5.6)

```{r practice of sf_Taiwan}

```