---
title: "課堂練習 20191030"
author: "Y.T Lin"
date: "2019/10/30"
output: html_document
---

```{r basic setup, message=FALSE, echo=TRUE, eval=T}
library(dplyr); library(stringr); library(ggplot2); library(plotly); library(lubridate); library(readr); library(tidyr); library(showtext); library(colorspace); library(scales)
font_add("QYuan","cwTeXQYuan-Medium.ttf") # 新增字體
showtext_auto(enable=TRUE) #啟用字體
theme_set(theme_classic())
knitr::opts_chunk$set(out.width='80%', fig.asp=.75, fig.align='center', fig.showtext=T)
```

## CH 4.2.5 stat_summary

We continue from last weeks lecture, now we proceed to talk about stat_summary().

```{r stat_summary}
market <- list()

market_demand <- function(x, a=1, b=-1){
  return(a+b*x)
}

market_supply <- function(x, a=0, b=1){
  return(a+b*x)
}

df_grids <- 
  data.frame(
    x=seq(0,1,by=0.2))

df_grids %>%
  ggplot(aes(x=x))+
  stat_function(
    fun="market_demand"
  )+
  stat_function(
    fun="market_supply"
  )+
  scale_y_continuous(
    limits = c(0,1)
  )+
  labs(
    x="Quantity", y="Price"
  ) -> market$demand_supply # draw the big X market graph

market$demand_supply

# add in the total welfare shade area
market$demand_supply+
  geom_ribbon(
    data=data.frame(
      x=seq(0.25,0.5,by=0.01)
    ),
    aes(y=x),
    stat="summary", 
    fun.ymin= function(y) market_demand(y),
    fun.ymax= function(y) market_supply(y),
    alpha=0.3
  )
```  
\  

## 4.3 some new stuff to play around

```{r new stuff}
d <- ggplot(diamonds, aes(carat, price))
d + geom_point() 

# turn the points in to hexagons
d + geom_hex(
  aes(fill=stat(density))
)
```  
\  

```{r the ggpubr pkg}
library(ggpubr)

graphList <- list()

df_position <- data.frame(
  x=rep(c("a","b"), each=3),
  y=c(3,1,3,8,6,10)
)

df_position %>%
  ggplot(aes(x=x,y=y))+
  geom_point(
    color="#5A99B3"
  ) + 
  scale_y_continuous(
    breaks=c(1,3,6,8,10)
  )+
  annotate(
    geom="text",
    x=1.1, y=3, label="x 2" # 利用factor的type為integer的特質設x位置
  )+
  labs(
    title="Position identity",
    subtitle="Position沒有調整"
    ) -> graphList$position_none

df_position %>%
  ggplot(aes(x=x,y=y,color=y))+
  geom_point(
    position="stack", color="#5A99B3"
  )+
  labs(
    title= "Position stack",
    subtitle = "各x類y值疊加上去" 
  )-> graphList$position_stack

ggpubr::ggarrange(
  graphList$position_none,
  graphList$position_stack
)
```  
\  

### 4.3.2 fill

```{r 432 fill}
df_position %>%
  ggplot(aes(x=x,y=y,color=y))+
  geom_point(
    position="fill", color="#5A99B3"
  )+
  labs(
    title= "Position fill",
    subtitle = "各x類y值縮放同比例使加總為1" 
  )-> graphList$position_fill

ggpubr::ggarrange(
  graphList$position_none,
  graphList$position_fill
)
```  
\  

### 4.3.3 dodge

```{r 433 dodge}
df_position %>%
  ggplot(aes(x=x,y=y))+
  geom_point(
    color="#5A99B3", alpha=0.3, size=4
  )+
  geom_point(
    position=position_dodge2(width=0.3), color="#5A99B3"
  )+
  labs(
    title= "Position dodge",
    subtitle = "淺色大圈為原始資料，\n深色小圈為position調整後" # \n 為換行符號
  )-> graphList$position_dodge

ggpubr::ggarrange(
graphList$position_none,
graphList$position_dodge
)
```  
\  

### 4.3.4 geom_bar playing around

```{r 434 data pulling, eval = F}
library(readr)
library100_102 <- read_csv("https://www.dropbox.com/s/wuo5o6l55lk68l6/library100_102.csv?dl=1")

# some simple data cleaning
library100_102 %>%
  mutate(
    借閱日期=date(ymd_hms(借閱時間)),
    借閱年=year(借閱日期)
  ) -> library100_102 # mutate the time data into date format (lubridate)

library100_102 %>%
  filter(
    借閱日期 %>% 
      dplyr::between(ymd("2014-09-01"),ymd("2015-06-30"))
  ) -> library2014  # between(data, x, y) , to choose the desired time line

library2014 %>%
  group_by(學號) %>%
  summarise(
    學院=last(學院),
    讀者年級=max(讀者年級)
  ) %>%
  ungroup() %>%
  mutate(
    讀者年級=as.factor(讀者年級)
    )-> library2014 

library2014 %>%
  mutate(
    學院=reorder(學院,學號,length,order=T)
    # order the 學院 via the student counts
  ) -> library2014
```

```{r 434 bar position = stack}

library2014 %>%
  ggplot(aes(x=學院,fill=讀者年級)) -> graphList$圖書_ggplotOnly_with_aes

graphList$圖書_ggplotOnly_with_aes +
  geom_bar() # 內定position="stack"
```  
\  

```{r bar position dodge}
graphList$圖書_ggplotOnly_with_aes +
  geom_bar(
    width=0.7, position = "dodge"
  ) -> # fill類別較少的,width會放大
  graphList$圖書_positionDodge

graphList$圖書_positionDodge


# Add in some spacings within bars

graphList$圖書_ggplotOnly_with_aes +
  geom_bar(
    width=0.7,
    position=position_dodge(width=0.8,preserve = "single") # 0.7寬，0.8dodge創造0.1間隔
  ) ->
  graphList$圖書_positionDodge_preserve

graphList$圖書_positionDodge_preserve

```  
\  

```{r bar position dodge refined}
# 電機、法律學院沒有1年級資料，count時會少一類並不會計0，造成圖面的不一致。此時建議自行count並以stat=“identity”方式作圖

library2014 %>%
  select(學院,讀者年級) %>%
  arrange(學院,讀者年級) %>%
  group_by(學院,讀者年級) %>%
  summarise(
    count=n()
  ) %>% ungroup() %>%
  add_row(
    學院=c("電機資訊學院","法律學院"),
    讀者年級=c(1,1),
    count=c(0,0)
  ) -> library2014count

library2014count %>%
  ggplot(aes(x=學院,fill=讀者年級)) -> graphList$圖書_ggplotOnly_with_aes2

graphList$圖書_ggplotOnly_with_aes2 +
  geom_bar(
    aes(y=count), ##### 指定高度y
    stat="identity", ##### 自行設定y時使用
    width=0.7,
    position=position_dodge(width=0.8) # 0.7寬，0.8dodge創造0.1間隔, preserve = "single"在類別齊全時可不用
  ) ->
  graphList$圖書_positionDodge2

graphList$圖書_positionDodge2
```  
\  

```{r prac for position dodge}
graphList$圖書_positionDodge2+
  geom_text(
    aes(y=count, label=count)
  ) -> graphList$圖書_positionDodge2_textExample

graphList$圖書_positionDodge2_textExample

graphList$圖書_positionDodge2+
  geom_text(
    aes(y=count, label=count), position = position_dodge(width = 0.8),
    vjust = - 0.5
  ) -> graphList$圖書_positionDodge2_textExample2

graphList$圖書_positionDodge2_textExample2
```  
\  

```{r bar position stack}
graphList$圖書_ggplotOnly_with_aes2 +
  geom_bar(
    stat="identity",
    aes(y=count), width=0.7, position="stack"
  )
```  
\  

```{r bar position stack add text}
graphList$圖書_ggplotOnly_with_aes2 +
  geom_bar(
    stat="identity",
    aes(y=count), width=0.7, position="stack"
  )+
  geom_text(
    aes(x=學院,label=count,y=count),
    position=position_stack(vjust=0.5),
    color="white"
  )
```  
\  

```{r add text via lable}
graphList$圖書_ggplotOnly_with_aes2 +
  geom_bar(
    stat="identity",
    aes(y=count), width=0.7, position="stack"
  )+
  geom_label(
    aes(x=學院,label=count,y=count),
    position=position_stack(vjust=0.5),
    color="white"
  )
```  
\  

There are still some other positions written in the bookdown, but it's getting boring. We will proceed into the subject of maps and spatial data.  
\  

## Ch5 maps and stuff  
\  

#### geom_line & geom_path

* geom_line: 以x值排序繪成。

* geom_path: 以(x,y)出現順序繪成。

```{r line and path difference}
df0 <- data.frame(
  x=c(1,2,1,3,2),
  y=c(2,3,1,2,4),
  label=c("a","b","c","d","e")
)
df0 %>%
  ggplot(aes(x=x,y=y))+
  geom_label(
    aes(label=label), fill="pink"
    )-> plotbase0

list_graphs <- list()

plotbase0+geom_line()+labs(title="geom_line") -> 
  list_graphs$geom_line

plotbase0+geom_path()+labs(title="geom_path") -> 
  list_graphs$geom_path

ggpubr::ggarrange(
  list_graphs$geom_line, list_graphs$geom_path
)
```  
\  

#### 5.1.1 Point, line, polygons
\  

We start off the topic of making the graph base, the grid lines.
Just for easier map construction sense, can later be deleted.  
\  

```{r make the base "mygrids"}
ggplot()+theme_linedraw()+
  scale_x_continuous(limits=c(0,6),breaks=0:6,
                     expand=expand_scale(add=c(0,0)))+
  scale_y_continuous(limits=c(0,6),breaks=0:6,
                     expand=expand_scale(mult = c(0,0))) ->
  myGrids

myGrids # simple and effable gridlines!

# theme_linedraw(), add in the lines for each tile.

# expand options to adjust the  xy axis to show position (0, 0)
```  
\  

```{r make points}
# make the points to be drawn

list_geometryData <- list()
list_geometryData$points <- 
  rbind(
    c(1,5),
    c(2,1),
    c(5,1),
    c(5,5)) 

list_geometryData$points %>%
  as.data.frame() 
```  
\  

The actual drawing in three different geoms  
\  

```{r map 3 approaches}
# location points
myGrids +
  geom_point(
    data=as.data.frame(list_geometryData$points),
    aes(x=V1,y=V2)
  ) -> list_graphs$point

# a route or a line connection of locations
myGrids +
  geom_path(
    data=as.data.frame(list_geometryData$points),
    aes(x=V1,y=V2)
  ) -> list_graphs$path

# An area of a region
myGrids +
  geom_polygon(
    data=as.data.frame(list_geometryData$points),
    aes(x=V1,y=V2)
  ) -> list_graphs$polygon

ggpubr::ggarrange(
  list_graphs$point, list_graphs$path, list_graphs$polygon,
  ncol=3
)
```

\  

#### 5.1.5 Practice

Draw a region of New Taipei City with geom_polygon.

```{r northTW prac}
library(readr)
df_geo_northTW <- read_csv("https://www.dropbox.com/s/6uljw24zkyj7avs/df_geo_northTW.csv?dl=1")

north <- df_geo_northTW %>% 
  filter(COUNTYNAME == "新北市")

north2 <- df_geo_northTW %>% 
  filter(COUNTYNAME == "新北市" | COUNTYNAME == "臺北市")

northTW <-ggplot() +
  geom_polygon(
    data=north,
    aes(x=x,y=y)
  ) + theme_linedraw()

northTW

northTW2 <-ggplot() +
  geom_polygon(
    data=north,
    aes(x=x,y=y)
  ) + theme_linedraw()

northTW2

```  
\  


```{r polygons with holes}
# Add in holes with options

list_graphs$polygon

list_geometryData$hole <-
  rbind(
    c(2,4),
    c(3,2),
    c(4,3)
  )

# BAD, not really solving the problem
list_graphs$twoPolygons <-
  list_graphs$polygon+
  geom_polygon(
    data=as.data.frame(list_geometryData$hole),
    aes(x=V1,y=V2), fill="white"
  )

ggpubr::ggarrange(
  list_graphs$polygon, list_graphs$twoPolygons
)

 # proper solving with options "subgroup"
list_geometryData$points %>%
  as.data.frame() -> df_part1
list_geometryData$hole %>%
  as.data.frame() -> df_part2

df_part1 %>%
  mutate(
    sub_id=1
  ) -> df_part1

df_part2 %>%
  mutate(
    sub_id=2
  ) -> df_part2

bind_rows(
  df_part1,
  df_part2
) -> df_all

df_all %>%
  mutate(
    group_id="A"
  ) -> df_all

# df_all

myGrids +
  geom_polygon(
    data=df_all,
    aes(x=V1,y=V2, group=group_id, subgroup=sub_id)
  )

df_all %>%
  add_row(
    V1=c(4,4.5,4.5),
    V2=c(1.5,1.5,2),
    sub_id=c(3,3,3),
    group_id="A"
  ) -> df_all3Subgroups

myGrids+
  geom_polygon(
    data=df_all3Subgroups,
    aes(
      x=V1,y=V2,group=group_id, subgroup=sub_id
    )
  )
```  
\  

```{r subgroup prac}

north3 <- df_geo_northTW %>% 
  filter(COUNTYNAME == c("新北市", "臺北市")) %>%
  mutate(
  group_id = "A",
  sub_id = case_when(
    COUNTYNAME == "新北市" ~ 1,
    T ~ 2,
  )
)

northTW3 <- ggplot() +
  geom_polygon(
    data=north3,
    aes(x=x,y=y,
        group = group_id,
    subgroup = sub_id)
  ) + theme_linedraw()

northTW3

#ALT approach

north2 <- df_geo_northTW %>% 
  filter(COUNTYNAME == "新北市" | COUNTYNAME == "臺北市")

northTW2 <-ggplot() +
  geom_polygon(
    data=north,
    aes(x=x,y=y)
  ) + theme_linedraw()

northTW2

```  
\  

#### 5.1.5 Multipolygons

```{r multipolygons}
df_geo_northTW %>%
  ggplot()+
  geom_polygon(
    aes(x=x,y=y,fill=COUNTYNAME), color="azure4"
  ) -> list_graphs$northTW

list_graphs$northTW

# add some annotations

# load(url("https://www.dropbox.com/s/9n7b1bcs09gnw0r/ggplot_newTaipei.Rda?dl=1")) # 前個練習若沒做出來，執行此行

list_graphs$northTW +
#  theme_linedraw()+
  geom_path(
    data=data.frame(
      x=c(121.55,121.7,121.9),
      y=c(25.1,24.7,24.7)
      ),
    aes(x=x,y=y)
    )+
  annotate(
    "text",
    x=121.9,y=24.71,label="這是臺北市",
    vjust=0
  )+
  theme_void()
```

#### 5.2.2 Adding pictures

We use `annotation_raster` to add in pictures. In the precedented cicumstance, you've used `PNG package` probably.

```{r}
library(magick)

download.file("https://mir-s3-cdn-cf.behance.net/project_modules/max_1200/2450df20386177.562ea7d13f396.jpg",
              destfile = "taipei101.jpg")

# or use image_read(), haha

image_read("https://mir-s3-cdn-cf.behance.net/project_modules/max_1200/2450df20386177.562ea7d13f396.jpg") -> taipei101

# check the image info
taipei101 %>%
  image_info() -> taipei101info

taipei101info

# 檢視圖片高寬比
taipei101info$height/taipei101info$width -> img_asp # image aspect ratio
img_asp

# needs to add in lost content (from adding the colored background)
```
